---
title: "API Practice"
format: html
editor: visual
---

-   Using `dataRetrieval` get the the discharge (ft³/s) time-series for the Ventura River (site `11118500`) during the recent Hilary tropical storm from 2023-08-19 to 2023-08-22

-   Plot the time-series usgin `ggplot2`

-   What was the maximum discharge during this period of time?

```{r}
library(dataRetrieval)
library(tidyverse)

siteNumber <- "11118500"
parameterCd <- "00060" # Discharge
startDate <- "2023-08-19"
endDate <- "2023-08-22"

discharge <- readNWISdv(siteNumber, parameterCd, startDate, endDate)

ggplot(discharge, aes(x = Date, y = discharge$X_00060_00003 )) + geom_line()

# Max discharge
max(discharge$X_00060_00003)


## 2023 January 9 storm

siteNumber2 <- "11118500"
parameterCd2 <- "00060" # Discharge
startDate2 <- "2023-01-08"
endDate2 <- "2023-01-12"

discharge_Jan <- readNWISdv(siteNumber2, parameterCd2, startDate2, endDate2)

ggplot(discharge_Jan, aes(x = Date, y = discharge_Jan$X_00060_00003 )) + geom_line() 


## Join 

data_compare <- full_join(discharge,discharge_Jan, 
                          by = join_by(site_no))

```

## Metajam

### **Exercise 2**

Let's determine what percentage of Alaskan household are speaking only English!

The data: https://doi.org/10.5063/F1N58JPP

1.  Read the metadata on the website

2.  Start a new R script and write a code to:

    -   download the data `household_language.csv` using `metajam`

    -   Read the data into R using `metajam`

    -   compute the percentage of Alaskan household speaking only English from 2009 to 2015

3.  Create a plot to visualize this data

```{r}
library(metajam)

url <- "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3A7fc6f6db-c5ea-426a-a743-1f2edafb43b8"

## save it to here directory
local_path <- "."

 metajam::download_d1_data(url, local_path)

```

Reading csv in R

```{r}

## this is a list with the metadata attached (units, names etc.)
 ak_household_data <- metajam::read_d1_files("doi_10.5063_F1N58JPP__household_language__csv/")
 


 
```

Compute the percentage of Alaskan household speaking only English from 2009 to 2015

```{r}
## Extract datafram out of the list
 
 data <- ak_household_data$data
 
 ## Percentage
 
 data_2009_20015 <- data %>% 
   # filter(Year %in% c(2009:2015))
   filter(Year >= "2009" & Year<= "2015") %>%
   #state level not city level
   group_by(Year) %>% 
   summarize(percent_english  = sum(speak_only_english)/sum(total))
 
 ##
  data_2009_20015_2 <- data %>% 
   # filter(Year %in% c(2009:2015))
   filter(Year >= "2009" & Year<= "2015") %>%
   #state level not city level
    mutate(only_english_percent = speak_only_english/total) %>% 
   group_by(Year) %>% 
   summarize(percent_english  = mean(only_english_percent, 
                                     na.rm =TRUE))
 
 
 ggplot(data_2009_20015, aes(x = Year, y = percent_english)) + geom_line()
```
